---
title: "London"
author: "Ana Real"
date: "June 4, 2019"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This work separates the universities in tops from the overall Rank variable:

* Top10 1-10.
* Top20 11-20.
* Top30 21-30.
* Top40 31-40.
* Top50 41-50.
* Top60 51-60.
* Top70 61-70.
* Top80 71-80.
* Top90 81-90.
* Top100 91-100.

Then some correlation plots were exported using this variables as groups.

## Read data

```{r read, warning=FALSE}
library(xlsx)
library(ggpubr)
library(DescTools)
library(xtable)
library(caret)
library(DMwR)
library(ggcorrplot)
library(corrplot)

data <- read.xlsx2("../final.xlsx", sheetIndex = 1)

for(i in c(1,2,4:10)){
    data[,i] <- as.numeric(as.character(data[,i]))
}

colnames(data) <- c("Year", "Rank", "City", "Overall", "Rankings", "Student.Mix", "Desirability", "Emp.Activity", "Affordability", "Student.View")

# Adding variable for top universities

data$Top <- data$Rank

for (i in 1:376){
    if (data$Rank[i] <= 10){
        data$Top[i] <- "Top10"
    } else if (data$Rank[i] > 10 & data$Rank[i] <= 20){
        data$Top[i] <- "Top20"
    } else if (data$Rank[i] > 20 & data$Rank[i] <= 30){
        data$Top[i] <- "Top30"
    } else if (data$Rank[i] > 30 & data$Rank[i] <= 40){
        data$Top[i] <- "Top40"
    } else if (data$Rank[i] > 40 & data$Rank[i] <= 50){
        data$Top[i] <- "Top50"
    } else if (data$Rank[i] > 50 & data$Rank[i] <= 60){
        data$Top[i] <- "Top60"
    } else if (data$Rank[i] > 60 & data$Rank[i] <= 70){
        data$Top[i] <- "Top70"
    } else if (data$Rank[i] > 70 & data$Rank[i] <= 80){
        data$Top[i] <- "Top80"
    } else if (data$Rank[i] > 80 & data$Rank[i] <= 90){
        data$Top[i] <- "Top90"
    } else {
        data$Top[i] <- "Top100"
    }
}
    
data$Top <- as.factor(data$Top)
str(data)
```

### Gruop Top10, top 10 cities.

```{r corr1, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr1 <- cor(data[data$Top=="Top10",c(4:10)], method="spearman")

ggcorrplot(corr1, lab = TRUE)

```

Some cities in this group:
* London
* Paris
* Tokyo


### Gruop Top20, cities from 11-20.

```{r corr2, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr2 <- cor(data[data$Top=="Top20",c(4:10)], method="spearman")

ggcorrplot(corr2, lab = TRUE)

```

Some cities in this group:

* Seoul
* Toronto
* New York

### Gruop Top30, cities from 21-30.

```{r corr3, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr3 <- cor(data[data$Top=="Top30",c(4:10)], method="spearman")

ggcorrplot(corr3, lab = TRUE)

```

Some cities in this group:
* Canberra
* Auckland
* Prague

### Gruop Top40, cities from 31-40.

```{r corr4, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr4 <- cor(data[data$Top=="Top40",c(4:10)], method="spearman")

ggcorrplot(corr4, lab = TRUE)

```

Some cities in this group:
* Barcelona
* Los Angeles
* Milan

### Gruop Top50,  cities from 41-50.

```{r corr5, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr5 <- cor(data[data$Top=="Top50",c(4:10)], method="spearman")

ggcorrplot(corr5, lab = TRUE)

```

Some cities in this group:
* Lyon
* Ottawa
* Budapest

### Gruop Top60, cities from 51-60.

```{r corr6, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr6 <- cor(data[data$Top=="Top60",c(4:10)], method="spearman")

ggcorrplot(corr6, lab = TRUE)

```

Some cities in this group:
* Mexico City
* Bangkok
* Philadelphia

### Gruop Top70, cities from 61-70.

```{r corr7, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr7 <- cor(data[data$Top=="Top70",c(4:10)], method="spearman")

ggcorrplot(corr7, lab = TRUE)

```

Some cities in this group:
* Dubai
* Oslo
* Rome

### Gruop Top80, cities from 71-80.

```{r corr8, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr8 <- cor(data[data$Top=="Top80",c(4:10)], method="spearman")

ggcorrplot(corr8, lab = TRUE)

```

Some cities in this group:
* Cape Town
* Athens
* Toulouse

### Gruop Top90, cities from 81-90.

```{r corr9, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr9 <- cor(data[data$Top=="Top90",c(4:10)], method="spearman")

ggcorrplot(corr9, lab = TRUE)

```

Some cities in this group:
* Bogota
* Monterrey
* Nanjing

### Gruop Top100, cities from 91-100.

```{r corr10, fig.height=5, fig.width=5, warning=FALSE}
# Using spearman

corr10 <- cor(data[data$Top=="Top100",c(4:10)], method="spearman")

ggcorrplot(corr10, lab = TRUE)

```

Some cities in this group:
* Mainla
* Mumbai
* Rio de Janeiro
