---
title: "Cross Validation"
author: "Ana Real"
date: "March 20, 2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This part of the project makes cross validation.

The idea is to have a set of trainning years and then a test set in the remaining year.

We are going to try holding four years and test in the remaining year. First leaving 2018 all the way to 2014 and try to guess a country in particular. In this case Toronto sice it appears all years.

We are using Mexico City as reference.

### Holdout : 2018

Training

```{r train1, cache=TRUE}
library(xlsx)
data <- read.xlsx2("cityData.xlsx", sheetIndex = 1)
for(i in c(1,3:9)){
    data[,i] <- as.numeric(as.character(data[,i]))
}
str(data)
# Removing 2018


data1 <- data[data$year!=2018,]

str(data1)
# Fitting the model

mexico <- relevel(data1$city, "Mexico City")
fit <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data1)
summary(fit)
coef1 <- summary(fit)$coef
```

Wtih this result we get the equation for Toronto: $0.96\times rankings + 1.03\times studentView + 0.87\times desirability + 1.19\times empActivity + 1.1\times affordability + 75.12 (Intercept)-13.39 (Toronto) = score$.
Substituting in out equation the 2018 data for Toronto.

```{r test1, cache=TRUE}
toronto2018 <- data[data$city=="Toronto"&data$year==2018,]

score <- coef1[2,1]*toronto2018$rankings + coef1[3,1]*toronto2018$student_view + coef1[4,1]*toronto2018$desirability + coef1[5,1]*toronto2018$emp_activity + coef1[6,1]*toronto2018$affordability + coef1[1,1] -13.39
score
toronto2018$overall

# Calculating the error

abs((score-toronto2018$overall)/toronto2018$overall)*100
```


### Holdout 2017:

Training

```{r train2, cache=TRUE}

# Removing 2017

data2 <- data[data$year!=2017,]

str(data2)
# Fitting the model

mexico <- relevel(data2$city, "Mexico City")
fit1 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data2)
summary(fit1)
coef2 <- summary(fit1)$coef
```


```{r test2, cache=TRUE}
toronto2017 <- data[data$city=="Toronto"&data$year==2017,]

score <- coef2[2,1]*toronto2017$rankings + coef2[3,1]*toronto2017$student_view + coef2[4,1]*toronto2017$desirability + coef2[5,1]*toronto2017$emp_activity + coef2[6,1]*toronto2017$affordability + coef2[1,1] -11.58
score
toronto2017$overall

# Calculating the error

abs((score-toronto2017$overall)/toronto2017$overall)*100
```


### Holdout 2016:

Training

```{r train3, cache=TRUE}

# Removing 2017

data3 <- data[data$year!=2016,]

str(data3)
# Fitting the model

mexico <- relevel(data3$city, "Mexico City")
fit3 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data3)
summary(fit3)
coef3 <- summary(fit3)$coef
```


```{r test3, cache=TRUE}
toronto2016 <- data[data$city=="Toronto"&data$year==2016,]

score <- coef3[2,1]*toronto2016$rankings + coef3[3,1]*toronto2016$student_view + coef3[4,1]*toronto2016$desirability + coef3[5,1]*toronto2016$emp_activity + coef3[6,1]*toronto2016$affordability + coef3[1,1] -8.97
score
toronto2016$overall

# Calculating the error

abs((score-toronto2016$overall)/toronto2016$overall)*100
```

### Holdout 2015:

Training

```{r train4, cache=TRUE}

# Removing 2017

data4 <- data[data$year!=2015,]

str(data4)
# Fitting the model

mexico <- relevel(data4$city, "Mexico City")
fit4 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data4)
summary(fit4)
coef4 <- summary(fit4)$coef
```


```{r test4, cache=TRUE}
toronto2015 <- data[data$city=="Toronto"&data$year==2015,]

score <- coef4[2,1]*toronto2015$rankings + coef4[3,1]*toronto2015$student_view + coef4[4,1]*toronto2015$desirability + coef4[5,1]*toronto2015$emp_activity + coef4[6,1]*toronto2015$affordability + coef4[1,1] -6.07
score
toronto2015$overall

# Calculating the error

abs((score-toronto2015$overall)/toronto2015$overall)*100
```

### Holdout 2014:

Training

```{r train5, cache=TRUE}

# Removing 2017

data5 <- data[data$year!=2014,]

str(data5)
# Fitting the model

mexico <- relevel(data5$city, "Mexico City")
fit5 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data5)
summary(fit5)
coef5 <- summary(fit5)$coef
```


```{r test5, cache=TRUE}
toronto2014 <- data[data$city=="Toronto"&data$year==2014,]

score <- coef5[2,1]*toronto2014$rankings + coef5[3,1]*toronto2014$student_view + coef5[4,1]*toronto2014$desirability + coef5[5,1]*toronto2014$emp_activity + coef5[6,1]*toronto2014$affordability + coef5[1,1] -6.07
score
toronto2014$overall

# Calculating the error

abs((score-toronto2014$overall)/toronto2014$overall)*100
```
