---
title: 'Linear regression: Experiment 1'
author: "Ana Real"
date: "March 19, 2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First Panel Data Experiment.

For this we are going to use the five years.

### Reading the data.

```{r read, cache=TRUE}
library(xlsx)
d2014 <- read.xlsx2("best_cities.xlsx", sheetIndex = 5)
d2015 <- read.xlsx2("best_cities.xlsx", sheetIndex = 4)
d2016 <- read.xlsx2("best_cities.xlsx", sheetIndex = 3)
d2017 <- read.xlsx2("best_cities.xlsx", sheetIndex = 2)
d2018 <- read.xlsx2("best_cities.xlsx", sheetIndex = 1)
```

### Looking at the data.

```{r head, cache=TRUE}
str(d2014)
str(d2015)
str(d2016)
str(d2017)
str(d2018)
```

### Preparing the data:

* Adding a year variable.
* Eliminating the rank variable.
* Change quality_living for desirability in 2014.
* Turning numeric variables to numeric.
* Adding student view variable to 2014-2016 data frames.
* Pasting the 5 data frames.

```{r year, cache=TRUE}
d2014$rank <- "2014"
d2014$student_view <- "0"
colnames(d2014) <- c("rank", "city", "overall", "rankings", "student_mix", "desirability", "emp_activity", "affordability", "student_view")
d2015$rank <- "2015"
d2015$student_view <- "0"
d2016$rank <- "2016"
d2016$student_view <- "0"
d2017$rank <- "2017"
d2018$rank <- "2018"
data <- rbind(d2018,d2017,d2016,d2015,d2014)
colnames(data) <- c("year", "city", "overall", "rankings", "student_mix", "desirability", "emp_activity", "affordability", "student_view")

# Looking at the data

head(data)
str(data)

# Turning variables to numeric

for(i in c(1,3:9)){
    data[,i] <- as.numeric(as.character(data[,i]))
}
str(data)

# Checking for NA's

sum(is.na(data$year))
sum(is.na(data$city))
sum(is.na(data$overall))
sum(is.na(data$rankings))
sum(is.na(data$student_mix))
sum(is.na(data$desirability))
sum(is.na(data$emp_activity))
sum(is.na(data$affordability))
sum(is.na(data$student_view))

# Exporting a xlsx file

write.xlsx2(data, "cityData.xlsx", sheetName = "panel", row.names = FALSE)
```

### First Data regression.

```{r fit, cache= TRUE}
fit <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view, data=data)
summary(fit)
```

### Adding cities as factors.

```{r fit1, cache= TRUE}
fit1 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+city, data=data)
summary(fit1)$coef
```

### Adding year as factor.

```{r fit2, cache= TRUE}
fit2 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+city+factor(year), data=data)
summary(fit2)
```

### Using Mexico City as reference.

```{r fit3, cache=TRUE}
mexico <- relevel(data$city, "Mexico City")
fit3 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+mexico+factor(year), data=data)
summary(fit3)
```

### Using London as reference.

```{r fit4, cache=TRUE}
london <- relevel(data$city, "London")
fit4 <- lm(overall~rankings+student_view+desirability+emp_activity+affordability+student_view+london+factor(year), data=data)
summary(fit4)
```